\section{Results}
\subsection{Main results (multi-seed where available)}
\begin{table}[h]
\centering
\begin{tabular}{ll}
\toprule
\input{tables/main_results.tex}
\bottomrule
\end{tabular}
\caption{Main results. Multi-seed entries report mean $\pm$ std and 95\% CI (n=5). Persistence and efficiency remain single-reference-run in this pass.}
\end{table}

\subsection{Interpretation}
ALC improves over the stale-memory baseline on core adaptation and on the added language-shaped delayed-recall benchmark. Stability remains strong in this suite (no NaN events across 10k-step stress runs in all seeds), and persistence round-trip remains exact in the reference run. Trainability improvements are consistent across seeds.

However, the no-write control is competitive and in some metrics stronger than full ALC, indicating that write-policy/interference remains an open issue. Therefore we frame evidence as mechanism-level: ALC can provide controlled adaptation benefits in this setup, but current results do not justify broad claims beyond this scope.

\subsection{Lightweight QA Benchmark}
\begin{table}[h]
\centering
\begin{tabular}{llll}
\toprule
\input{tables/tinyqa_results.tex}
\bottomrule
\end{tabular}
\caption{Lightweight Tiny-QA-style benchmark under delayed recall. Values are QA accuracy (mean $\pm$ std across 5 seeds).}
\end{table}

This semi-realistic QA evaluation adds evidence beyond purely synthetic recall probes. In this setup, ALC full improves delayed QA accuracy over baseline and no-write controls at non-zero delays, while absolute accuracies remain modest; we therefore treat these results as directional mechanism evidence rather than broad language QA claims.

\subsection{Ablations}
Ablation results over slot count, update rate, routing mode, and fusion mode are exported to \texttt{paper/tables/ablation\_results.csv}. The top-10 single-run ablations are listed below.

\begin{table}[h]
\centering
\begin{tabular}{ll}
\toprule
\input{tables/ablation_top10.tex}
\bottomrule
\end{tabular}
\caption{Top-10 ablation variants by recall MSE in the reference run (lower is better).}
\end{table}
